---
title: "Book title"
subtitle: "Book subtitle"
author: "Authors"
site: bookdown::bookdown_site
output: 
    bookdown::gitbook:
        css: style.css
        number_sections: false
        anchor_sections: false
        split_by: chapter
        config:
            sharing:
                 github: no
                 facebook: no
                 twitter: no
                 all: no
            toc:
                collapse: section
                scroll_highlight: yes
                before: <li class="toc-logo"><a href="./"></a> <h4 class=".paddingtitel ">BOOK_ACRONYM</h2></li>
header-includes:
  - \usepackage{fontawesome5}
---

```{r include = FALSE}
# set CSS for objects
knitr::opts_chunk$set(
  class.source="Rchunk", 
  class.output="Rout", 
  warning = FALSE,
  error = FALSE,
  message = FALSE)
```

```{r include = FALSE}
# Define the web addresses for the course
# run as needed
githuburl <- "<github_url>"
readerurl <- "https://rstudio-connect.hu.nl/rmd-vhp4safety/"
email <- "email_contactperson"

save(
    list = c("githuburl", "readerurl", "email"), 
    file = "course_urls.RData")
```

# Book Intro

Download the source code [`r icons::fontawesome("github")`](<github_url>)

## RMarkdown and Quatro documentation
See for additional info: 

https://bookdown.org/yihui/rmarkdown/

https://quarto.org/

## Let's build a report
We use data from the [TOXRIC](https://toxric.bioinforai.tech/download) database. See for more details: [Wu et al., 2023]( https://doi.org/10.1093%2Fnar%2Fgkac1074)

## Packages
```{r}
library(tidyverse)
library(tidymodels)
```

## Data
In chapter 1,  we will use toxicity data from experiments with _Daphnia magna_ and Fathead minnow. Both datasets can be downloaded from the `TOXRIC` database, and are stored as CSV file sin the `./data-raw` folder. We will combine the data into one dataset, after some preprocessing.

In chapter 2, we will use the famous Gapminder dataset. See also: https://www.gapminder.org/ 
